---
title: "central_dogma"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{central_dogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AnalysisCD)
```

Jose

We sample a random string of ATCGs to create DNA. For this we use the function ..., with a parameter that tells us the length of the DNA string.

```{r}
dna_string <- dna_sequence(2000)
dna_string
```

Judith

```{r}
rna_string <- replace_T_with_U(dna_string)
rna_string

```

Emilie

```{r}
codons <- get_codons(rna_string)
codons
```

Sahand

```{r}

codons_str <- codons_to_aa_sequence(codons)
codons_str
```

Felix

The last function of the package is the plot_codons function. It takes a string of aminoacids (single letter format) without space as parameter. An example could be this: "VADEGTSNK". This plots the amino acids generated by the former functions, in a nice way. Alternatively, a string of amino acids gathered from elsewhere can also be used in the function.

Test
```{r}
plot_codons(codons_str)

```
