---
title: "central_dogma"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{central_dogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## AnalysisCD Package

The AnalysisCD Package can be used to analyse the central dogma. It includes a set of functions which ...

```{r setup}
library(AnalysisCD)
```

#### A random DNA sequence

Jose

We sample a random string of ATCGs to create DNA. In the functoin a sting is generated where replica is set to true. This means there will not be an equal number of bases in the sequence. The function takes a number as input, a prarameter representing the length of the wanted DNA sequence. This function is important because it quickly creates new, random stings which can be used as input for other functions. Because the user may decide the lenght, it gives the opportunity to make a short sequence, which is easy to read. Playing around with this sequence as input to other functions, will give the opportunity to understand what happens. On the other hand, creating a long string will make it realsitic and representative of real life. 
```{r}
dna_string <- dna_sequence(200)
dna_string
```

#### Converting DNA  to RNA

judith

```{r}
rna_string <- replace_T_with_U(dna_string)
rna_string

```

#### Transform RNA to codons 

The function get_codons takes an input of a string of an RNA sequence and the first base pair to be included. It returns a list of codons that the sequence translates to.

```{r}
codons <- get_codons(rna_string)
codons
```

#### Title for this function

Sahand

Would look at function and consider renaming it :D

```{r}

codons_str <- codons_to_aa_sequence(codons)
codons_str
```

#### Plotting amino acids from codons

The last function of the package is the plot_codons function. It takes a string of codons without space as parameter. An example could be this: "VADEGTSNK". This plots the codons generated by the former functions, in a nice way. Alternatively, a string of codons gathered from elsewhere can also be used in the function.

```{r}
plot_codons(codons_str)

```
