---
title: "central_dogma"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{central_dogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## AnalysisCD Package

The AnalysisCD Package can be used to analyse the central dogma. It includes a set of functions which ...

```{r setup}
library(AnalysisCD)
```

#### A random DNA sequence

Jose

We sample a random string of ATCGs to create DNA. For this we use the function ..., with a parameter that tells us the length of the DNA string.

```{r}
dna_string <- dna_sequence(200)
dna_string
```

#### Converting DNA  to RNA

judith

```{r}
rna_string <- replace_T_with_U(dna_string)
rna_string

```

#### Transform RNA to codons 

The function get_codons takes an input of a string of an RNA sequence and the first base pair to be included. It returns a list of codons that the sequence translates to.

```{r}
codons <- get_codons(rna_string)
codons
```

#### Title for this function

Sahand

Would look at function and consider renaming it :D

```{r}

codons_str <- codons_to_aa_sequence(codons)
codons_str
```

#### Plotting amino acids from codons

The last function of the package is the plot_codons function. It takes a string of codons without space as parameter. An example could be this: "VADEGTSNK". This plots the codons generated by the former functions, in a nice way. Alternatively, a string of codons gathered from elsewhere can also be used in the function.

```{r}
plot_codons(codons_str)

```
